\chapter{详细代码分析}
\label{ch:src}



\begin{XeClass}{ChecksumFSOutputSummer}
This class provides an output stream for a checksummed file.
    \begin{XeMethod}{\XePublic}{void}{setVerifyChecksum}
        Set whether to verify checksum.
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{FileSystem}{getRawFileSystem}
        
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{Path}{getChecksumFile}
        
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{boolean}{isChecksumFile}
        
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{long}{getChecksumFileLength}
        Return the length of the checksum file given the size of theactual file./
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{int}{getBytesPerSum}
        
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{long}{skip}
        Skips over and discards <code>n</code> bytes of data from theinput stream.*he <code>skip</code> method skips over some smaller number of byteswhen reaching end of file before <code>n</code> bytes have been skipped.The actual number of bytes skipped is returned.  If <code>n</code> isnegative, no bytes are skipped.*ChecksumException if the chunk to skip to is corrupted
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{void}{seek}
        Seek to the given position in the stream.The next read() will be from that position.<p>This method does not allow seek past the end of the file.This produces IOException.*ChecksumException if the chunk to seek to is corrupted
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{FSDataInputStream}{open}
        Opens an FSDataInputStream at the indicated Path.
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{FSDataOutputStream}{append}
        
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{long}{getChecksumLength}
        Calculated the length of the checksum file in bytes.
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{FSDataOutputStream}{create}
        
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{boolean}{setReplication}
        Set replication for an existing file.Implement the abstract <tt>setReplication</tt> of <tt>FileSystem</tt>false if file does not exist or is a directory
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{boolean}{rename}
        Rename files/dirs
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{boolean}{delete}
        Implement the delete(Path, boolean) in checksumfile system.
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{FileStatus[]}{listStatus}
        List the statuses of the files/directories in the given path if the path isa directory.given path
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{void}{copyToLocalFile}
        The src file is under FS, and the dst is on the local disk.Copy it from FS control to the local dst name.
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{void}{copyToLocalFile}
        The src file is under FS, and the dst is on the local disk.Copy it from FS control to the local dst name.If src and dst are directories, the copyCrc parameterdetermines whether to copy CRC files.
    \end{XeMethod}

    \begin{XeMethod}{\XePublic}{boolean}{reportChecksumFailure}
        Report a checksum error to the file system.
    \end{XeMethod}

\end{XeClass}
